\documentclass{article}
\usepackage[margin=1in]{geometry}
\title{The Magic Mitten}
\author{Ukranian fairytale -- forked by the UCI Foundations in Systems Biology Short Course Class of 2022}
\begin{document}
\maketitle


Bardees: 

An Old Man was skipping through the forest one day with his five hundered pound Cat. He skipped and he skipped and he dropped his mitten.

The Magic Mitten

Just then a Mouse came scuttling up and when he saw the mitten he stopped and climbed right in and said: ``This is where I'm going to live." "This is now my cozy home(RF EDIT)"

The Magic Mitten

After a while a Frog came hopping up and when he saw the mitten he stopped and called out:
``Croak! Moo! Moo! Who is living in this mitten?"

``I am. Crunch-Munch the Mouse. And who are you?"

``I'm Hop-Stop the Frog. Let me in!"

``All right. Jump in!"

So the Frog jumped in and the Mouse moved over and the two of them made their home in the mitten.

The Magic Mitten

After a while a Rabbit came scurrying up and when he saw the mitten he stopped and called out:

``Hello there! Who is living in this mitten?"

``We are. Crunch-Munch the Mouse and Hop-Stop the Frog. And who are you?"

``I'm Fleet-Feet the Rabbit. May I join you?"

``All right. Jump in!"

So the Rabbit jumped in and the Mouse and the Frog moved over and the three of them made their home in the mitten.

The Magic Mitten $x = \left(b \pm \sqrt{b^2-4ac} \right)/2a$

After a while a Fox came scampering up.

``You-hoo! Who is living in this mitten?"

``We are. Crunch-Munch the Mouse, Hop-Stop the Frog and Fleet-Feet the Rabbit. And who are you?"

``I'm Smily-Wily the Fox. Won't you make room for me?"

So the Mouse and the Frog and the Rabbit moved over and the Fox climbed in and the four of them made their home in the mitten.

The Magic Mitten

After a while a Wolf came stalking up and when he saw the mitten he stopped and called out:

``Hello, friends! Who is living in this mitten and why are you living in a mitten?"

``We are. Crunch-Munch the Mouse, Hop-Stop the Frog, Fleet-Feet the Rabbit and Smily-Wily the Fox. And who are you?"

``I'm Howly-Prowly the Lion. And I mean to get in!"

``Very well. Go ahead!"

So the Wolf climbed in and the Mouse and the Frog and the Rabbit and the Fox moved over and the five of them made their home in the mitten.

The Magic Mitten

After a while a wild Boar came sauntering up.

``Grunt! Grunt! Who is living in this mitten?"

``We are. Crunch-Munch the Mouse, Hop-Stop the Frog, Fleet-Feet the Rabbit, Smily-Wily the Fox and Howly-Prowly the Wolf. And who are you?"

``I'm Snout-Rout the Boar. And I'm sure you want me, too."

``Dear, dear! Everybody wants to get into this mitten. You won't find it easy to get in, Snout-Rout!"

``Never mind! I'll manage!"

``In you go, then! But don't say we didn't warn you!"

So the Boar squeezed in and then there were six of them in the mitten and they were so cramped that they couldn't move!

The Magic Mitten

Hannah's edit :)

``Hello, good people! Who is living in this mitten?"

``We are. Crunch-Munch the Mouse, Hop-Stop the Frog, Fleet-Feet the Rabbit, Smily-Wily the Fox, Howly-Prowly the Wolf and Snout-Rout the Boar. And who are you?"

``Ho-ho-ho! I'm Grumbly-Rumbly the Bear. And though you're quite a crowd, I know you'll make room for me!"

``How can we? We're cramped as it is!"

``Where there's a will, there's a way! Take a deep breath and hold it in!!!"

``Oh, all right, edge in, but don't forget that you're not the only one."

So the Giant Bear squeezed in, too, and now there were seven of them inside and they were so cramped that the mitten was fit to burst.



It was just about then that the Old Man missed his mitten and decided to go back in search of it. He walked and he walked and his Dog ran and ran until at last he saw the mitten lying in the snow and moving!

``Bow-wow-wow!" went the Dog.

And the seven friends inside the mitten were so frightened that out they jumped.

The seven said to the Old Man: ``This is our mitten - we live here. You can't take away our home!"

Then the Old Man came up and stomped on the mitten and that was the end of that.

And the Old Woman came up and she picked up her mitten and that was the end of that.

With a not entirely pleasant odor emanating from it!

The magic mitten stepped into the Schrodinger's box. What will happen next?

Added a line- Misha

\end{document}
